Code used to generate paper results : Database comparison and CT characteristics

### 2023-09-18 Paper_code-Database_CT.Rmd
small change in TCGA_expression

genes <- CT_genes$external_gene_name
database <- database[rowData(database)$external_gene_name %in% genes, ]
database <- database[match(genes, rowData(database)$external_gene_name), ]

column_ha_type <- HeatmapAnnotation(
  Type = database$type,
  border = TRUE,
  col = list(Type = c("Tumor" = "salmon",
                      "Peritumoral" = "mediumseagreen")),
  annotation_name_gp = gpar(fontsize = 8),
  annotation_legend_param = legends_param)

>>>>

genes <- CT_genes$external_gene_name
database <- database[rowData(database)$external_gene_name %in% genes, ]
database <- database[match(genes, rowData(database)$external_gene_name), ]
database <- database[, database$type == "Tumor"]
